Figure 6. Differential Protein expression

### 2022-08-24 reports/manuscript/Figure1.Rmd
Change figure format to tiff, jpeg and pdf

---
title: "Figure 1.Luminal Study Groups"
geometry: "left=2cm,right=2cm,top=2cm,bottom=2cm"
output: 
  pdf_document:
    fig_caption: yes
header-includes: 
- \usepackage{float}
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  fig.width = 6.6929133858,
  fig.path="./Figures/",
  dev=c('pdf', 'png'), dpi=300,
  fig.process = function(filename){
    new_filename <- stringr::str_remove(string = filename, 
                                        pattern = "-1")
    fs::file_move(path = filename, new_path = new_filename)
    ifelse(fs::file_exists(new_filename), new_filename, filename)

      # Create PNG
      # path2 <- xfun::with_ext(new_filename, "png")
      # img <- magick::image_read(new_filename)
      # magick::image_write(img, path2, format = "png")
})
# setwd("/Users/vilkal/work/Brolidens_work/Projects/broliden_5325/reports/manuscript")

#### Figure requirements Microbiome: ####
  # - width of 85 mm for half page width figure
  # - width of 170 mm for full page width figure
  # - maximum height of 225 mm for figure and legend
  # - image resolution of approximately 300 dpi (dots per inch) at the final size
```

```{r Load data, message=FALSE, warning=FALSE, include=FALSE}
##################
# LOAD LIBRARIES #
##################
suppressWarnings({suppressMessages({suppressPackageStartupMessages({
  library(tidyverse)
  library(scales)
  library(igraph)
  library(RColorBrewer)
  #remotes::install_github("czarnewski/niceRplots",force=T)
  library(niceRplots)
  library(openxlsx)
})  })  })

@@

```{r Figure 1, echo=FALSE, fig.pos="t", fig.height=6.2, message=FALSE, warning=FALSE}
# , fig.height=6.2
figlabels <- letters
# fig.height=7, fig.asp=1,
print(knitr::is_latex_output())
layout(matrix(c(1,1,1,1,1,1,
                2,2,2,2,2,2,
                3,3,3,3,3,3,
                5,6,7,7,8,8,
                5,4,7,7,8,8,
                5,4,7,7,8,8) , ncol= 6,byrow = T),
                               widths = c(1.87,1.42,.7,.8,.8,.7,.8),
                               heights = lcm(c(4.7,2,4.5,2,.5)) # height in cm
                              # heights = c(1.4,.55,1.4,.61,.75,0)
       ) 
### A
#################################
# COHORT SCHEMATIC ILLUSTRATION #
#################################
par(mar=c(0.1,3.7,0.3,1)) #b,l,t,r
plot(c(0,1),c(0,1),axes=F,type="n",xlab="",ylab="",xaxs="i",yaxs="i")
rasterImage(fig1a, 0, 0, 1, 1)

@@

```{r Suppl. Table 1., include=FALSE}
# Total Relative Abundance 
raw <- c("ASV_Luminal", "ASV_Tissue") %>% set_names()
raw_list <- raw %>%
  map(., ~read_csv(paste0("../../results/02_data_preprocessing_output/",.x,"_raw_counts.csv")))  %>%
  map(., ~column_to_rownames(., var = "X1")) %>%          
  map(., ~dplyr::select(., any_of(sample_use)))

@@

pages <- list("Total Relative Abundance"=r ,"Alfa Diversity"=div_stat, "Bacterial Communities"=bac_communities)
write.xlsx(pages, file=paste0(result_dir,"Suppl.Tbl.01",".xlsx"))

>>>>

---
title: "Figure 1.Luminal Study Groups"
geometry: "left=2cm,right=2cm,top=2cm,bottom=2cm"
header-includes: 
- \usepackage{float}
editor_options: 
  chunk_output_type: console
knit: (function(inputFile, out_dir, ...) {
    source("../../code/knit_function.R");
    custom_knit(inputFile, "../../lab_book/Figure1/", ...)
    })
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  results = "hold",
  message    = FALSE,
  warning    = FALSE,
  fig.width = 6.6929133858,
  fig.path="./Figures/",
  fig.process = function(filename){
    new_filename <- stringr::str_remove(string = filename, 
                                        pattern = "-1")
    fs::file_move(path = filename, new_path = new_filename)
    ifelse(fs::file_exists(new_filename), new_filename, filename)
})
# setwd("/Users/vilkal/work/Brolidens_work/Projects/broliden_5325/reports/manuscript")
#.libPaths("/Users/vilkal/Applications/miniconda3/envs/Paulos_repo/lib/R/library")

#### Figure requirements Microbiome: ####
  # - width of 85 mm for half page width figure
  # - width of 170 mm for full page width figure
  # - maximum height of 225 mm for figure and legend
  # - image resolution of approximately 300 dpi (dots per inch) at the final size

```{r Load data}
##################
# LOAD LIBRARIES #
##################
suppressWarnings({suppressMessages({suppressPackageStartupMessages({
  library(tidyverse)
  library(scales)
  library(igraph)
  library(RColorBrewer)
  #remotes::install_github("czarnewski/niceRplots",force=T)
  library(niceRplots)
  library(openxlsx)
})  })  })

@@

```{r Figure 1, fig.align = "center", fig.pos="t", fig.height=6.2}
# , fig.height=6.2
# fig.height=7, fig.asp=1,
figlabels <- letters

layout(matrix(c(1,1,1,1,1,1,
                2,2,2,2,2,2,
                3,3,3,3,3,3,
                5,6,7,7,8,8,
                5,4,7,7,8,8,
                5,4,7,7,8,8) , ncol= 6,byrow = T),
                               widths = c(1.87,1.42,.7,.8,.8,.7,.8),
                               heights = lcm(c(4.7,2,4.5,2,.5)) # height in cm
                              # heights = c(1.4,.55,1.4,.61,.75,0)
       ) 
### A
#################################
# COHORT SCHEMATIC ILLUSTRATION #
#################################
par(mar=c(0.1,3.7,0.3,1)) #b,l,t,r
plot(c(0,1),c(0,1),axes=F,type="n",xlab="",ylab="",xaxs="i",yaxs="i")
rasterImage(fig1a, 0, 0, 1, 1)

@@

```{r Suppl. Table 1.}
# Total Relative Abundance 
raw <- c("ASV_Luminal", "ASV_Tissue") %>% set_names()
raw_list <- raw %>%
  map(., ~read_csv(paste0("../../results/02_data_preprocessing_output/",.x,"_raw_counts.csv")))  %>%
  map(., ~column_to_rownames(., var = "X1")) %>%          
  map(., ~dplyr::select(., any_of(sample_use)))

@@

pages <- list("Total Relative Abundance"=r ,"Alfa Diversity"=div_stat, "Bacterial Communities"=bac_communities)
write.xlsx(pages, file=paste0(result_dir,"Suppl.Tbl.01",".xlsx"))
alpa_div <- set_names(div_list, c("Luminal","Tissue"))
write.xlsx(alpa_div, file=paste0(result_dir,"alpha_diversity",".xlsx"))
```

```{r eval=FALSE, include=FALSE}
#############
# TOP DGEs #
#############
p_val <- pull(top, "PValue")
top_dge <- (p_val < 0.01) #& (rowSums( abs(top[,grep("logFC",colnames(top))]) >= log2(1.5) ) >= 1)
top_dge <- top$Genes[ top_dge ]

top_TRX_counts <- edgeR::cpm(y,normalized.lib.sizes = T,log = T)[top_dge, ]
top_TRX_counts <- t(apply(top_TRX_counts,1,function(x){scale(x,T,T)}))
top_TRX_counts[top_TRX_counts > 5] <- 5
colnames(top_TRX_counts) <- colnames(TRX_counts)

##########################
# UMAP ON TOP DGE RNAseq #
##########################
mypar(2,3,mar=c(2,2,2,6))
set.seed(1)
UMAP_TRX <- uwot::umap(t(top_TRX_counts),n_neighbors = 10,
                 metric = "correlation",min_dist = 0.1,spread = 5,
                 negative_sample_rate = 10)
plot(UMAP_TRX,bg=pal[group_annotation[sample_use]],main="UMAP on top DGE RNAseq",
     pch=21,xlab="UMAP1",ylab="UMAP2",frame=F,axes=F)
legend(par("usr")[2],par("usr")[4],title.adj = 0,
       legend = levels(factor(group_annotation)),xjust = 0,yjust = 1,
       bty = "n",pch = 21,pt.bg = pal,pt.cex = 1,xpd=T)
```

### 2022-08-24 reports/manuscript/Figure4-5.Rmd
Change figure format to tiff, jpeg and pdf

---
title: "Figure 4. & 5. DGE's and Enrichment"
geometry: "left=2cm,right=2cm,top=2cm,bottom=2cm"
output: 
  pdf_document:
    fig_caption: yes
header-includes: 
- \usepackage{float}
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  fig.width = 6.6929133858,
  fig.path="./Figures/",
  dev=c('pdf', 'png'), dpi=300,
  fig.process = function(filename){
    new_filename <- stringr::str_remove(string = filename, 
                                        pattern = "-1")
    fs::file_move(path = filename, new_path = new_filename)
    ifelse(fs::file_exists(new_filename), new_filename, filename)
})
# setwd("/Users/vilkal/work/Brolidens_work/Projects/broliden_5325/reports/manuscript")
```

```{r message=FALSE, warning=FALSE, include=FALSE}
##################
# LOAD LIBRARIES #
##################
suppressWarnings({suppressMessages({suppressPackageStartupMessages({
  library(tidyverse)
  library(edgeR)
  library(openxlsx)
  library(scales)
  library(RColorBrewer)
  #remotes::install_github("czarnewski/niceRplots",force=T)
  library(niceRplots)
  library(readxl)
  library(enrichR)
  library(igraph)
  library(rafalib)
})  })  })

@@

## Heatmap DGEs and enrichment
```{r Across functions, message=FALSE, warning=FALSE, include=FALSE}
##################
# DEG's FUNCTION #
##################
#group <- "Tissue_gr"
#group <- "Luminal_gr"
edgR_dge.fun <- function(group, confound) {

@@

```{r Pairwise functions, message=FALSE, warning=FALSE, include=FALSE}
###########################
# PAIRWISE DEG's FUNCTION #
###########################
pairwise_dge.fun <- function(group, fit, design) {
  groups <- metadata[sample_use, group]
  levels <- as.character(sort(unique(groups),na.last = NA))

@@

```{r Across tables, fig.height=4, fig.width=7, warning=F, include=FALSE}
TRX <- datasets_all_samples[["Tissue_RNAseq_V3_normalized"]]
TRX_counts <- round(2^TRX - 1)
TRX_counts <- TRX_counts [ rowSums(TRX_counts>0)>= 1 , ]
TRX_counts <- TRX_counts[,sample_use]

@@

```{r Pairwise tables, include=FALSE}
##################
# PAIRWISE DEG's #
##################
pairwise_dge_L <- pairwise_dge.fun(group = "Luminal_gr", 
                                   fit=dge_L$fit, 
                                   design=dge_L$design )
pairwise_dge_T <- pairwise_dge.fun(group = "Tissue_gr",
                                   fit=dge_T$fit,
                                   design=dge_T$design)

@@

```{r Suppl. Tbl. 4 & 8, include=FALSE}
# DEG's across and pairwise
pages <- list(list(Across=dge_L$top), pairwise=pairwise_dge_L$top) %>% flatten()
write.xlsx(pages, file=paste0(result_dir,DEG_files[1]))

@@

```{r Suppl. Tbl. 5,6 & 9,10, eval=FALSE, include=FALSE}
# Enrichment Across
df_across <- enframe(list(Luminal=enrich_L, Tissue=enrich_T)) %>%  
  unnest_longer(value) %>%
  mutate(res = map(.$value, "res_list")) %>%
  unnest_longer(res) %>%
  mutate(res = map(res, ~rownames_to_column(.x, var = "Terms"))) %>%
  mutate(res = map(res, ~filter(.x, pvalue <= 0.01))) %>%
  group_by(name, value_id) %>%
  mutate(mod = row_number()) %>% ungroup() %>%
  mutate(res = set_names(.$res, paste0(.$value_id,"_gene_module_",.$mod))) %>%
  group_split(name) %>% set_names(., map(., ~unique(.x$name)))

@@

```{r Suppl. Tbl. 12, include=FALSE}
metadata <- metadata %>% 
  mutate(L_T_groups = paste0(.$Luminal_gr, .$Tissue_gr)) %>%
  mutate(L_T_groups = ifelse(grepl("L2T2|L2T3", .$L_T_groups), .$L_T_groups, NA))

@@

## igraph network plot
```{r igraph network, eval=FALSE, warning=FALSE, include=FALSE}
# 1. Change the groups of interest by assigning condition_use
# 2. Change the number of genes to be included in the network by changing n
#    look at tempD_i and tempU_i to see how many genes was significant
# 3. Adjust the size of the gene nodes and text in the graph by changing; square, circle and txt

>>>>

---
title: "Figure 4. & 5. DGE's and Enrichment"
geometry: "left=2cm,right=2cm,top=2cm,bottom=2cm"
header-includes: 
- \usepackage{float}
editor_options: 
  chunk_output_type: console
knit: (function(inputFile, out_dir, ...) {
    source("../../code/knit_function.R");
    custom_knit(inputFile, "../../lab_book/Figure4-5/", ...)
    })
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  results = "hold",
  message    = FALSE,
  warning    = FALSE,
  fig.width = 6.6929133858,
  fig.path="./Figures/",
  fig.align = "center",
  fig.process = function(filename){
    new_filename <- stringr::str_remove(string = filename, 
                                        pattern = "-1")
    fs::file_move(path = filename, new_path = new_filename)
    ifelse(fs::file_exists(new_filename), new_filename, filename)
})
# setwd("/Users/vilkal/work/Brolidens_work/Projects/broliden_5325/reports/manuscript")
```

```{r message=FALSE, warning=FALSE}
##################
# LOAD LIBRARIES #
##################
suppressWarnings({suppressMessages({suppressPackageStartupMessages({
  library(tidyverse)
  library(edgeR)
  library(openxlsx)
  library(scales)
  library(RColorBrewer)
  #remotes::install_github("czarnewski/niceRplots",force=T)
  library(niceRplots)
  library(readxl)
  library(enrichR)
  library(igraph)
  library(rafalib)
})  })  })

@@

## Heatmap DGEs and enrichment
```{r Across functions, message=FALSE, warning=FALSE}
##################
# DEG's FUNCTION #
##################
#group <- "Tissue_gr"
#group <- "Luminal_gr"
edgR_dge.fun <- function(group, confound) {

@@

```{r Pairwise functions, message=FALSE, warning=FALSE}
###########################
# PAIRWISE DEG's FUNCTION #
###########################
pairwise_dge.fun <- function(group, fit, design) {
  groups <- metadata[sample_use, group]
  levels <- as.character(sort(unique(groups),na.last = NA))

@@

```{r Across tables, fig.height=4, fig.width=7, warning=F}
TRX <- datasets_all_samples[["Tissue_RNAseq_V3_normalized"]]
TRX_counts <- round(2^TRX - 1)
TRX_counts <- TRX_counts [ rowSums(TRX_counts>0)>= 1 , ]
TRX_counts <- TRX_counts[,sample_use]

@@

```{r Pairwise tables}
##################
# PAIRWISE DEG's #
##################
pairwise_dge_L <- pairwise_dge.fun(group = "Luminal_gr", 
                                   fit=dge_L$fit, 
                                   design=dge_L$design )
pairwise_dge_T <- pairwise_dge.fun(group = "Tissue_gr",
                                   fit=dge_T$fit,
                                   design=dge_T$design)

@@

```{r Suppl. Tbl. 4 & 8}
# DEG's across and pairwise
pages <- list(list(Across=dge_L$top), pairwise=pairwise_dge_L$top) %>% flatten()
write.xlsx(pages, file=paste0(result_dir,DEG_files[1]))

@@

```{r Suppl. Tbl. 5,6 & 9,10, eval=FALSE}
# Enrichment Across
df_across <- enframe(list(Luminal=enrich_L, Tissue=enrich_T)) %>%  
  unnest_longer(value) %>%
  mutate(res = map(.$value, "res_list")) %>%
  unnest_longer(res) %>%
  mutate(res = map(res, ~rownames_to_column(.x, var = "Terms"))) %>%
  mutate(res = map(res, ~filter(.x, pvalue <= 0.01))) %>%
  group_by(name, value_id) %>%
  mutate(mod = row_number()) %>% ungroup() %>%
  mutate(res = set_names(.$res, paste0(.$value_id,"_gene_module_",.$mod))) %>%
  group_split(name) %>% set_names(., map(., ~unique(.x$name)))

@@

```{r Suppl. Tbl. 12}
metadata <- metadata %>% 
  mutate(L_T_groups = paste0(.$Luminal_gr, .$Tissue_gr)) %>%
  mutate(L_T_groups = ifelse(grepl("L2T2|L2T3", .$L_T_groups), .$L_T_groups, NA))

@@

## igraph network plot
```{r igraph network, eval=FALSE, warning=FALSE}
# 1. Change the groups of interest by assigning condition_use
# 2. Change the number of genes to be included in the network by changing n
#    look at tempD_i and tempU_i to see how many genes was significant
# 3. Adjust the size of the gene nodes and text in the graph by changing; square, circle and txt

### 2022-08-24 reports/manuscript/Figure6.Rmd
Change figure format to tiff, jpeg and pdf

---
title: "Figure 6. Differential Protein expression"
geometry: "left=2cm,right=2cm,top=2cm,bottom=2cm"
output: 
  pdf_document:
    fig_caption: yes
header-includes: 
- \usepackage{float}
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  fig.width = 6.6929133858,
  fig.path="./Figures/",
  dev=c('pdf', 'png'), dpi=300,
  fig.process = function(filename){
    new_filename <- stringr::str_remove(string = filename, 
                                        pattern = "-1")
    fs::file_move(path = filename, new_path = new_filename)
    ifelse(fs::file_exists(new_filename), new_filename, filename)
})
# setwd("/Users/vilkal/work/Brolidens_work/Projects/broliden_5325/reports/manuscript")
```

>>>>

---
title: "Figure 6. Differential Protein expression"
geometry: "left=2cm,right=2cm,top=2cm,bottom=2cm"
header-includes: 
- \usepackage{float}
editor_options: 
  chunk_output_type: console
knit: (function(inputFile, out_dir, ...) {
    source("../../code/knit_function.R");
    custom_knit(inputFile, "../../lab_book/Figure6/", ...)
    })
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  results = "hold",
  message    = FALSE,
  warning    = FALSE,
  fig.width = 6.6929133858,
  fig.path="./Figures/",
  fig.align = "center",
  fig.process = function(filename){
    new_filename <- stringr::str_remove(string = filename, 
                                        pattern = "-1")
    fs::file_move(path = filename, new_path = new_filename)
    ifelse(fs::file_exists(new_filename), new_filename, filename)
})
# setwd("/Users/vilkal/work/Brolidens_work/Projects/broliden_5325/reports/manuscript")
```
